Modelling the gas kinematics of an atypical Lyman alpha emitting compact dwarf galaxy

### 2017-07-02 paper/paper.tex
updated caption
minor typos

The observed flux for the \lya line is $\sim
8.1\times 10^{-14}$ erg cm$^{-2}$ s$^{-1}$ \citep{Thuan97}.
The \lya Equivalent Width is $70$\AA\ and its H$\beta$ flux is 
$1.62\times 10^{-14}$ erg cm$^{-2}$ s$^{-1}$ \AA${-1}$
which gives a \lya/H$\beta$ flux ratio of
4.9$\pm$0.1 \citep{Izotov04}.
Comparing the \lya/H$\beta$ ratio with the theoretical
expectation from case B recombination of $23.3$ \citep{Hummer1987} one
can estimate an escape fraction of $20$\% for \lya radiation.

@@

Using the total number of degrees of freedom, $d.o.f.=104$ we divide
the results in two classes: low $\chi^2/d.o.f.<35$ and high
$\chi^2/d.o.f.35>$. 
We apply a random forest classification algorithm to find the
more relevant parameters in splitting the results into these two
classes. 
The algorithm uses $500$ trees for the classification and a
maximum of $3$ depth levels. 
To check for stability we repeat the computation $10$ times by
randomly subsampling the input data to use $80\%$ of the data as
the training set.

@@

\begin{figure}
\begin{center}
\includegraphics[width=0.46\textwidth]{enclosed_mass.pdf}
\caption{Enclosed mass in a spherical system as a function of radius.
  Lines correspond to the expectation for dark matter halos and the point
  to the dynamical mass lower bounds for \tol.
  The dynamical mass estimates for \tol\ are consistent with the
  galaxy being hosted by a dark matter halo of at least
  $6\times10^{11}$ M$_{\odot}$ in mass.
    \label{fig:mass}} 
\end{center}
\end{figure}

>>>>

The observed flux for the \lya line is $\sim
8.1\times 10^{-14}$ erg cm$^{-2}$ s$^{-1}$ \citep{Thuan97}.
The \lya Equivalent Width is $70$\AA\ and its H$\beta$ flux is 
$1.62\times 10^{-14}$ erg cm$^{-2}$ s$^{-1}$ \AA$^{-1}$
which gives a \lya/H$\beta$ flux ratio of
4.9$\pm$0.1 \citep{Izotov04}.
Comparing the \lya/H$\beta$ ratio with the theoretical
expectation from case B recombination of $23.3$ \citep{Hummer1987} one
can estimate an escape fraction of $20$\% for \lya radiation.

@@

Using the total number of degrees of freedom, $d.o.f.=104$ we divide
the results in two classes: low $\chi^2/d.o.f.<35$ and high
$\chi^2/d.o.f.>35$. 
We apply a random forest classification algorithm to find the
more relevant parameters in splitting the results into these two
classes. 
The algorithm uses $500$ trees for the classification and a
maximum of $3$ depth levels. 
To check for stability we repeat the computation $10$ times by
randomly subsampling the input data to use $80\%$ of the data as
the training set.

@@

\begin{figure}
\begin{center}
\includegraphics[width=0.46\textwidth]{enclosed_mass.pdf}
\caption{Enclosed mass in a spherical system as a function of radius.
  Lines correspond to the expectation for dark matter halos with
  different viral masses as shown in the legend, the arrow corresponds
  to the dynamical mass lower bounds for \tol.  
  The dynamical mass estimates for \tol\ are consistent with the
  galaxy being hosted by a dark matter halo of at least
  $6\times10^{11}$ M$_{\odot}$ in mass.
    \label{fig:mass}} 
\end{center}
\end{figure}
